\Title

### 2020-12-16 manuscript/manuscript.tex
Make a list of steps to setup windows and layers

We can transform our equivalent source problem in
equation~\ref{eq:linear-problem} into an additive model by
(1) defining a set of $K$ overlapping windows of equal size that cover the
survey area and (2) defining one set of equivalent sources per
window. Then, the coefficients $\mathbf{c}_k$ relate to the equivalent sources
of the $k$-th window and $\mathbf{A}_k$ is the Jacobian matrix between
those sources and every data point.
Thus, the predicted data are a superposition of the
effects of the $K$ sets of equivalent sources.

The gradient boosting algorithm above works by fitting each component of the
additive model, one at a time, to the residuals of the previous component.
\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
optimization in the so-called ``function space'', with $\alpha_k$ corresponding
to step sizes in steepest descent.
We can modify the gradient boosting algorithm of \citet{friedman2001} to
find the damped least-squares solutions for the $K$ parameters vectors
$\mathbf{c}_k$ and step sizes $\alpha_k$ in equation~\ref{eq:gb-linear-model}:

@@

    \nllabel{alg:residual}
    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient boosting solution for damped least-squares regression.}
\end{algorithm}

\citet{friedman2002} suggests that introducing randomness into the fitting
process can improve convergence of the solution. To achieve this, we randomize
the order in which the $K$ windows are used in the gradient boosting algorithm.

@@

\subsection{Source distributions}

>>>>

We can transform our equivalent source problem in
equation~\ref{eq:linear-problem} into an additive model by following these
steps:

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source-distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window, by
    taking from the original set of $M$ sources the ones that fall within the
    respective windows. Since the windows overlap, the total number of sources
    from all sets will be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

The gradient boosting algorithm works by fitting each component of the
additive model, one at a time, to the residuals of the previous component.
\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
optimization in the so-called ``function space'', with $\alpha_k$ corresponding
to step sizes in steepest descent.
The adaptation of the gradient boosting method to find the damped least-squares
solutions for the $K$ parameters vectors $\mathbf{c}_k$ and step sizes
$\alpha_k$ in equation~\ref{eq:gb-linear-model} is presented in
Algorithm~\ref{alg:gradient_boosting}.

@@

    \nllabel{alg:residual}
    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient boosting solution for damped least-squares regression.}
  \label{alg:gradient_boosting}
\end{algorithm}

To improve the convergence of the algorithm, \citet{friedman2002} suggests that
introducing randomness into the fitting process. We achieve this by randomizing
the order in which the $K$ windows are used in the gradient boosting algorithm.

@@

\subsection{Source distributions}
\label{sec:source-distribution}
